Build azimuth compatible fetal kidney reference from the kidney cell atlas

### 2024-08-09 analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Update analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Co-authored-by: Jaclyn Taroni <19534205+jaclyn-taroni@users.noreply.github.com>

We save it in the marker-sets folder of the module.
Note to the DataLab: should we save it somewhere else? 
I suggest this rds file could be placed here transiently and removed once the reference is build?

```{r path_to_data}
path_to_data <- file.path(module_base, "marker-sets/fetal_full.rds")

>>>>

We place it in the `scratch` folder of the module because it is a temporary file.

```{r path_to_data}
path_to_data <- file.path(module_base, "scratch", fetal_full.rds")
